The COVID-19 Pandemic impact on bullying search intensity relate with Asian population

### 2023-02-21 Outputs/Paper/paper.qmd
update title

---
title: "Analysis on The COVID-19 Pandemic Disrupted Both School Bullying and Cyberbullying"
subtitle: "My subtitle if needed"
author: 
  - Will Davidson
  - Jason Ngo
  - Annie Yan
thanks: "Code and data are available at: https://github.com/AnnieYan0807/Analysis-on-The-COVID-19-Pandemic-Disrupted-Both-School-Bullying-and-Cyberbullying."
date: "`r Sys.time()`"
date-format: "D MMMM YYYY"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

>>>>

---
title: "The COVID-19 Pandemic impact on bullying search intensity relate with Asian population"
author: 
  - Will Davidson
  - Jason Ngo
  - Annie Yan
thanks: "Code and data are available at: https://github.com/AnnieYan0807/Analysis-on-The-COVID-19-Pandemic-Disrupted-Both-School-Bullying-and-Cyberbullying."
date: "`r Sys.time()`"
date-format: "D MMMM YYYY"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---
